\cvsection{work experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cloud Architect} % Job title
    {DXC Technology} % Organization
    {Rome -- Italy} % Location
    {April 2017 -- now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Multi-private cloud post-sales detailed solution \& implementation (Scalr, VMware, OpenStack, Juniper Contrail).}
        \item {AWS hub/spoke deployment with a transit VPC based on Check Point CloudGuard. Hybrid network connection with customers's HQs. Multi-region 1:1 disaster recovery.}
        \item {VMware + VMware on AWS distributed hybrid cloud architecture under a single Scalr cloud management platform. End-to-end responsibility on the technical proposal. Core/edge computing model. Orchestration framework based on Scalr+Terraform integration.}
        \item {Architectural design and cost modeling for a dual-AZ VMware on AWS deployment.}
        \item {Dry-run sessions with the VMware on AWS offering team for an end-to-end documentation quality walkthrough.}
        \item {Solution design, migration planning and execution for a Government Authority portal and relevant integrations within a private cloud based on OpenStack.}
        \item {For an EMEA customer, end-to-end accountability on a multi-region AWS solution with common Organizations layout and general network layout based on multiple Direct Connect gateways. Security, network and VPC design. Full logical security layout using AWS Organizations and IAM policies. Integration and orchestration artifacts via DXC Private Cloud solution and its own portal. Full analysis on the SNOW's ITSM capabilities and full-working orchestration proof of concept.}
        %\item {For an italian oil\&gas customer, dual-site Red Hat Openstack architecture and proposal with underpinning block, object and image Ceph stretched cluster.}
        \item {Within the italian automotive context, architecture definition and proposal of a Container as a Service internal solution - based on Docker, Swarm and a custom CI/CD pipeline, developed and maintained by local delivery teams. Cost modeling and transition planning.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Information Systems Architect} % Job title
    {Hewlett Packard Enterprise} % Organization
    {Rome} % Location
    {2009 -- April 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Part of the SPC Cloud development team. Main contributions: Oracle PaaS catalog, relevant licensing and restricted workload placement, underpinning technical architecture, cost and price modeling. Also, I worked for enabling a custom dual-site OpenStack deployment with Disaster Recovery capabilities. SPC Cloud is a community cloud solution for Gov't agencies (federal, central) based on HPE Helion Openstack and custom requirements.}
        \item {Docker \& Swarm multi-node deployment underpinning a long-running training service for the Ministry of Justice.}
        \item {Application containerization within a virtual private cloud, for a banking application.}
        \item {VPC architecture, migration planning, cost modeling and IaaS setup enabling a SAP relocation two different EMEA \& UK customers.}
        \item {Disaster Recovery for a core service of the Ministry of Justice, between two main DCs, using VMware SRM. End-to-end task including requirements definition, target architecture (under and over DR), relationships with internal and external stakeholders including vendors, and team leadership.}
        \item {Multi-node VMware deployment and Oracle RAC deployment for a Gov't agency: project and technical management.}
%        \item {Innovapuglia}
%        \item {SKF}
%        \item {VMware + RAC per MdG}
%        \item {ESA WPS encryption}
%        \item {ESA FTP extension}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Technical Architect, Systems Engineer and previous roles} % Job title
    {EDS Electronic Data Systems} % Organization
    {Rome, Milan} % Location
    {2000 -- 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Corporate e-mail system head of service delivery and contiuous improvement. Integration between commercial \& open source products.}
				\item {UNIX \& Linux systems modeling, software packaging and automated deploying for the Ministry of Education.}
				\item {Systems modeling and hardening for the 2004 \& 2005 electronic polling experimentations by the Italian Government: I developed the OS part of the e-vote kiosks.}
				\item {For Fata Informatica: Technical trainer (classroom) on Java, C, C++, and consultant on systems engineering and service administration for the Ministry of Education}
				\item {For Frama Development (Milan): programmer on CRM and DWH solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
